Are you moving predictably?

### 2018-07-11 dokumentation/data_findings.tex

\end{figure}
\begin{figure}[H]
	\centering

	\centering
	\includegraphics[width=3.0in]{../Martin-RapidMiner/diagramme/origin_destination_reason_lowJitter.png}
	\caption{Reason for movements from origin to destination}
	\label{fig:origin_destination_reason}

\end{figure}
	\end{minipage}
\begin{minipage}{0.48\textwidth}
	We are looking for clusters inside the whole dataset by generating different charts which visualize a subset of attributes of all data points. Firstly, before neglecting the strata data of the data set, we consider chart \ref{fig:strata_reason_age} which visualizes the different reasons why people move at which age grouped by socio-economic classes. Throughout the classes each cloud of points is very similar, i. e. young people are mostly studying, adults are mostly working and older people are moving for recreation or health. Therefore categorizing people by taking the reason for their movements into account is not an option. The only difference that is not caused by outliers is the smaller size of the first and last economic class.\\

>>>>

\end{figure}
	\end{minipage}
\begin{minipage}{0.48\textwidth}

	We are looking for clusters inside the whole dataset by generating different charts which visualize a subset of attributes of all data points. Firstly, before neglecting the strata data of the data set, we consider chart \ref{fig:strata_reason_age} which visualizes the different reasons why people move at which age grouped by socio-economic classes. Throughout the classes each cloud of points is very similar, i. e. young people are mostly studying, adults are mostly working and older people are moving for recreation or health. Therefore categorizing people by taking the reason for their movements into account is not an option. The only difference that is not caused by outliers is the smaller size of the first and last economic class.\\

### 2018-07-11 dokumentation/submission.tex

		\keywords{Data Mining \and Clustering \and Rapidminer \and Cluster \and Neural Nets} %TODO: maybe more
	\end{abstract}
	%
	%
	%
	\section{Introduction}
	%	TODO (1 page)
	% could at more in depth 
	Within the time of Industry 4.0 and various data sources the question arises, if one can define who we are by the data collected? In particular is it possible to determine the wealth of a person, only given movements of a single day?
	For this we considered the dataset stated in \cite{rich_do_not_rise_early}. There we have a set of 124979 rows of movement data from various persons from a Columbian town, called Medellín. All the data was collected at a single day, with possibly multiple entries referring to the same person.\\
	The data entries consist of data about the movement, like endpoints or length, and also some meta parameters like gender, age or the so-called strata of the person. The strata defines the socio-economic group, reflecting the affluence and therefore impose the ancillary costs.\\
	Our goal is to ascertain if there is a correlation between the movements and the strata.

@@

	\subsection{Distance Measures}
	%TODO: distance measures
	TODO (1 page)

	\subsection{Classification}
	%TODO: clustering
	TODO (5 pages)	
	%	\input{MiriamClustering}
	\subsection{Neural Net}
	For all the neural net computations we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\

@@

	\section{Observations}
	%	TODO (1 page)
	%	TODO: restructure. Have like 3 parts
	%	The greater the population, the more the borders between the stratas blur. 
	As an overall result we get, that we can not determine the strata based on the information we have.
	Using various datasets (c.f. \Cref{sec: proprocessing}), we witnessed that having equally distributed datasets lead to an overall higher accuracy. This rules out the bias observed in the original data, where strata 2 and 3 are very dominant (c.f. \Cref{table: distribution normal}), but also reduces the set size from originally 124978 to $6*2038=12228$ entries equally distributed over all stratas.\\
	During clustering we observed, that using a different distance measure formula would not lead to a huge difference. Also, we detected that reducing the numbers of clusters leads to better results, which reduces the significance of result that could be stated.\\
	Using a different neural net architecture will most likely not chance the accuracy value drastically. As stated, more complex nets need more training data, which is restricted as mentioned above.\\
	What we can observe is, that using the stratified vectors, we are able to increase the performance and accuracy, but still have no sufficient predictions. Therefore we see that the more data we have the higher the variance within the stratas themselves is. We cannot draw some kind of lines to distinguish between different entries. Datapoints, which were outliers in the smaller sets, are now not considered to be outliers, because of large numbers having the same characteristics. So the lines, we were able to draw for smaller datasets, are blurring and create some kind of transition phase.\\ %TODO: letzter satz doof

	\section{Discussion}
	%TODO: discussion
	TODO (2 page)

>>>>

		\keywords{Data Mining \and Clustering \and Rapidminer \and Cluster \and Neural Nets} %TODO: maybe more
	\end{abstract}
	%
	%
	%
	\section{Introduction} \label{sec: introduction}
	%	TODO (1 page)
	% could at more in depth 
	Within the time of Industry 4.0 and various data sources the question arises, if one can define who we are by the data collected? In particular is it possible to determine the wealth of a person, only given movements of a single day?
	For this we considered the dataset stated in \cite{rich_do_not_rise_early}. There we have a set of 124979 rows of movement data from various persons from a Columbian town, called Medellín. All the data was collected at a single day, with possibly multiple entries referring to the same person.\\
	The data entries consist of data about the movement, like endpoints or length, and also some meta parameters like gender, age or the so-called strata of the person. The strata defines the socio-economic group, reflecting the affluence and therefore impose the ancillary costs.\\
	Our goal is to ascertain if there is a correlation between the movements and the strata.

@@

	\subsection{Distance Measures} \label{subsec: distance measures}
	%TODO: distance measures
	TODO (1 page)

	\subsection{Classification} \label{subsec: classification}
	%TODO: clustering
	TODO (5 pages)	
	%	\input{MiriamClustering}
	\subsection{Neural Net} \label{subsec: neural net}
	For all the neural net computations we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\

@@

	\section{Observations} \label{sec: observation}
	%	TODO (1 page)
	%	TODO: restructure. Have like 3 parts
	%	The greater the population, the more the borders between the stratas blur. 
	As an overall result we get, that we can not determine the strata based on the information we have.
	Using various datasets (c.f. \Cref{sec: proprocessing}), we witnessed that having equally distributed datasets lead to an overall higher accuracy. This rules out the bias observed in the original data, where strata 2 and 3 are very dominant (c.f. \Cref{table: distribution normal}), but also reduces the set size from originally 124978 to $6*2038=12228$ entries equally distributed over all stratas.\\
	During clustering we observed, that using a different distance measure formula would not lead to a huge difference. Also, we detected that reducing the numbers of clusters leads to better results, which reduces the significance of result that could be stated.\\
	Using a different neural net architecture will most likely not chance the accuracy value drastically. As stated, more complex nets need more training data, which is restricted as mentioned above.\\
	What we can observe is, that using the stratified vectors, we are able to increase the performance and accuracy, but still have no sufficient predictions. Therefore we see that the more data we have the higher the variance within the stratas themselves is. We cannot draw some kind of lines to distinguish between different entries. Datapoints, which were outliers in the smaller sets, are now not considered to be outliers, because of large numbers having the same characteristics. So the lines, we were able to draw for smaller datasets, are blurring and create some kind of transition phase.\\ %TODO: letzter satz doof

	\section{Discussion} \label{sec: discussion}
	%TODO: discussion
%	TODO (2 page)
%	\begin{itemize}
%		\item repr. working day
%		\item over/under std's
%		\item indiv. of lifestyle
%		\item inv. behaviour in same strata
%	\end{itemize}
	Regarding the results, of not predicting the strata and also not observing any meaningful clusters throughout the data in given and stratified form, we though about various aspects having an impact on the movement. We state 4 main influencing aspects, explaining the variance throughout the data.

	\subsection{Representativity of the day}
	The day the data was collected on (c.f. \Cref{sec: introduction}) is not mentioned. Therefore we can not infer that it is representative. The people asked to enter their movement could have a exceptional day, like a vacation day, a doctors appointment or a broken car and therefore behave different from a usual day. \\
	Also the day itself is not mentioned, so we don't have information if it was even a working day or a weekend. This influences the behavior drastically.

	\subsection{People living over/under standards}
	%TODO

	\subsection{Individuality of lifestyle}
	Obviously, people are individual in their way of life. So there are people, with enough money to buy for example a car, but refuse to in order to reduce CO$_2$ emission, or simply don't like driving. On the other end of the spectrum, some people, who have little money still own and drive a car daily in order to go to work, since they can't afford an other apartment.\\
	One can think of multitude scenarios, of people behaving different, cause by their individuality.

	\subsection{Inverse behavior in a strata}
	As an example, take a look at the strata 6, which denotes the richest people considered. Their we have inter alia two groups: 
	\begin{enumerate}
		\setlength{\itemindent}{1cm}
		\item[1. Group]
		Hard working people, laboring 60+ hours per weak to earn their money. One can imagine that they have to move quite a lot since they are always busy.
		\item[2. Group]
		People, who are rich just by birth, which don't have the necessity to work or move at all. They could possibly stay home and don't have to leave at all.
	\end{enumerate} 
	Those two groups are completely opposite, but still belong to the same strata. Now also considering strata one, we can find the exact same movement behavior in there as well. Within the poorest there are people that are wandering around the town via feet or bike, since they have no objective, like work. Also there are people, who don't move at all, because of the same reason.

	So we can see that based on the information we have it is very unlikely to have a precise correlation between the given data and the strata. However given more information about the previously mentioned aspects and more entries in general there could be some kind correlation to be found.\\
	Future work could include a component analysis of the decision tree and neural network in order to ascertain the influencing parts and therefore improve the data gathering. Also one could use different network visualization tools in order to infer their own patterns. An example would be to take the origin (destination) sectors as nodes, an edge if there is a movement, directed or undirected, and a different thickness or color gradient based on the number of this edge being taken.\\

	Overall we can conclude that with the data we got we are not able to find a correlation.
